Compositional Certified Resource Bounds

### 2015-04-09 paper/main.tex
layout work, not so bad now!

>>>>

The rule {\sc Q:Loop} is a cornerstone of our analysis.  To apply it on a
loop body one needs to find an invariant potential $Q$ that will pay for
the iterations.  At each iteration, $M_l$ resources are spent to jump back,
this explains the postcondition $Q{+}M_l$. %  Assuming $M_l>0$, and if $Q$
%is finite on the initial heap (i.e. the precondition is not $\bot$), the
%loop can only run for a finite number of iterations.
To exit the loop,
the programmer uses the \code{break} statement, this explains why the postcondition
for the full $\code{loop}~S$ statement $\{ \Gamma'; Q' \}$ is used as break
postcondition in the derivation for $S$.
